### 2015-05-14 Draft/approach.tex
Formatted to fit in 10 page format
Closes #8

\begin{figure}
	\centering
		\includegraphics[scale=0.45]{approach.eps}
	\caption{Overview of the \tool\ approach}
	\label{fig:approachOverview}
\end{figure}

@@

\begin{figure}
	\centering
		\includegraphics[scale=0.25]{StanfordAnnotated.eps}
	\caption{Sentence annotated with Stanford dependencies}
	\label{fig:standep}
\end{figure}

@@

2) \textbf{Sentence Type}: The context of sentence, whether the sentence appears as method summary, parameter summary, return value summary, or exception/error summary as captured by pre-processor phase. The rationale is that a majority of the temporal constraint sentences are either summary or exception sentences.

@@

As described in Section~\ref{sub:SENLPback} the intermediate representation generation technique is implemented as a function of Stanford-typed dependencies~\cite{Marneffe06LREC,Marneffe08COLING,KleinNIPS03}, to leverage the semantic information encoded in Stanford-typed dependencies.

However, we observed that such implementation is overwhelmed by complex sentences.
We improve the accuracy of intermediate-representation generation by proposing a hybrid approach, i.e. taking into consideration both the POS tags as well as Stanford-typed dependencies.
The POS tags which annotate the syntactical structure of a sentence are used to further simplify the constituent elements in a sentence. 
We then use the Stanford-typed dependencies that annotate the grammatical relationships between words to construct our FOL like representation.
Thus, the intermediate representation generator used in this work is a two phase process as opposed to single phase in previous work~\cite{pandita12:inferring, pandita13:WHYPER}. 
We next describe these two phases:

{\small $\bullet$} \textbf{POS Tags}: We first parse a sentence based on the function of POS tags. 
In particular, we use semantic templates to logically break a sentences into smaller constituent sentences. 
For instance, consider the sentence which are then accurately annotated by the underlying NLP Parser:

@@

The Stanford parser faces difficulty to annotate accurately the Stanford-typed dependencies of the sentence because of presence of various clauses acting on various subject-object pairs.
As shown in Figure~\ref{fig:standep} the word including is annotated with Stanford-typed dependencies ``dep'' that is a catch all dependency. A catch all dependency is selected by a parser when no other appropriate dependency can be selected.
The \tool\ approach thus automatically break down the sentence into two smaller tractable sentences:

@@

\begin{table*}
\begin{center}

\caption{Semantic Templates}
    \begin{tabular}{  l  p{5cm} p{10cm} }
    \topline
    \headcol  \textbf{S No.} 	& \textbf{Template} & \textbf{Summary} \\
    \midline

    		1. 		& Two sentences joined by a conjunction & Sentence is broken down into two individual sentences with the conjunction term serving as the connector between two. \\
\rowcol    	2. 		& Two sentences joined by a ``,''& Sentence is broken down to individual independent sentences \\
    		3.		& A noun phrase followed by another noun/pronoun/verb phrase in brackets & Two individual sentences are formed. The first sentence is the same as the parent sentence sans the noun/pronoun.verb phrase in bracket. The second sentence constitutes of the noun phrase followed by noun/pronoun/verb phrase without the brackets.\\
\rowcol    	4.		& A noun phrase by a conditional phrase in brackets & Two individual sentences are formed. The first sentence is the same as the parent sentence sans the conditional phrase in bracket. The second sentence constitutes of noun phrases followed by conditional in the bracket.\\ 
    		5.		& A conditional phrase followed by a sentence & Two dependent sentences are formed. The first sentence constitutes the conditional phrase. The second sentence constitutes rest of the sentence.\\
\rowcol    	6.		& A sentence in which the parent verb phrase is over two child verb phrases joined by a conjunction & Two dependent sentences are formed where the dependency is the conjunction. The first sentence is formulated by removing conjunction and second child verb phrase. The second sentence is formulated by removing conjunction and first child verb phrase. \\ 
\bottomlinec
    \end{tabular}
	\label{tab:semanticTemplates}
\end{center}
\end{table*}

@@

\begin{figure}
	\begin{CodeOut}
		\begin{alltt}
			01:before[6]
			02:|->must be deleted[5]
			03:\hspace*{0.2in}|->All[1]
			04:\hspace*{0.2in}|\hspace*{0.2in}|->in[3]
			05:\hspace*{0.2in}|\hspace*{0.4in}|->\textbf{objects}[2]
			06:\hspace*{0.2in}|\hspace*{0.4in}|->\textbf{bucket}[4]
			07:\hspace*{0.2in}|->can be deleted[8]
			08:\hspace*{0.4in}|->\textbf{bucket}[7]
			09:\hspace*{0.4in}|->\textbf{itself}[9]
		\end{alltt}
	\end{CodeOut}
	\caption{\label{fig:FOLTree} FOL representation of the sentence \textit{``All objects in the bucket must be deleted before the bucket itself can be deleted.''}}
\end{figure}

@@

1) \textit{Forward Operator ($\xi_1 \rightarrow \xi_2$)}: method call $\xi_1$ must be succeeded by method call $\xi_2$.

2) \textit{Backward Operator ($\xi_1 \leftarrow \xi_2$)}: method call $\xi_1$ must be preceded by method call $\xi_2$.

3) \textit{Negative Forward Operator ($\xi_1 \xrightarrow{-} \xi_2$)}: method call $\xi_1$ cannot be succeeded by method call $\xi_2$

4) \textit{Negative Backward Operator ($\xi_1 \xleftarrow{-} \xi_2$)}: method call $\xi_1$ cannot be preceded by the method call of $\xi_2$

%The prohibition operators capture a different class of temporal constraints that cannot be
%expressed by the formulae constructed by previously proposed operators and their negations.
%For instance, the \textit{prohibition operators} seem to be negation of
%\textit{forward eventual operators} and \textit{backward eventual operators}.
%However, the negation of forward eventual operators is: not an invocation of $\xi_1$
%must be eventually followed by not an invocation of $\xi_2$. In contrast,
%\textit{prohibition operators} either negates antecedent or consequent but not both.
%In summary, we extended the formalism for temporal rules previously
%proposed by Lo et al.~\cite{lo2009mining} to express temporal constraints.

We next show how \tool\ identifies the terms of the constraint formula:

@@

\textbf{Temporal Operator}:
\tool\ next identifies the direction (forward or backward) of the relationship by examining the tense of $\xi_2$ reference in the sentence.
Past tense is considered as backward and other tenses are considered as forward.
For instance, the sentence in Figure~\ref{fig:standep} since ``deleted'' is in past tense and therefore operator is backward and the constraint is 
Delete Bucket $\leftarrow$ Delete Object.

The negation is identified by presence of the negation verbs such as ``\textit{no}'', ``\textit{not}'', ``\textit{can't}'' ... etc.
Another rule for negation operator is if the sentence is in exception/error description.

@@

\begin{figure}
	\centering
	\includegraphics[scale=0.3]{KnowledgeGraph.eps}
	\caption{Semantic Graph for the \CodeIn{Object} related operations in Amazon S3 REST API}
	\label{fig:knowledge}
\end{figure}

>>>>

\begin{figure}
	\centering
		\includegraphics[scale=0.45]{approach.eps}
	\vspace*{-2ex}
	\caption{Overview of the \tool\ approach}
	\label{fig:approachOverview}
	\vspace*{-4ex}
\end{figure}

@@

\begin{figure}
	\centering
		\includegraphics[scale=0.25]{StanfordAnnotated.eps}
	\vspace*{-2.5ex}
	\caption{Sentence annotated with Stanford dependencies}
	\label{fig:standep}
	\vspace*{-3ex}	
\end{figure}

@@

2) \textbf{Sentence Type}: The context of sentence, whether the sentence appears as under method, parameter, return value, or exception/error summary as captured by pre-processor phase. The rationale is that a majority of the temporal constraint sentences are either method or exception summary sentences.

@@

Section~\ref{sub:SENLPback} the intermediate representation generation technique implemented as a function of Stanford-typed dependencies~\cite{Marneffe06LREC,Marneffe08COLING,KleinNIPS03}, to leverage the semantic information encoded in Stanford-typed dependencies.
However, we observed that such implementation is overwhelmed by complex sentences.
We improve the accuracy of intermediate-representation generation by proposing a hybrid approach, i.e. taking into consideration both the POS tags as well as Stanford-typed dependencies.
The POS tags which annotate the syntactical structure of a sentence are used to further simplify the constituent elements in a sentence. 
We then use the Stanford-typed dependencies that annotate the grammatical relationships between words to construct our FOL like representation.
Thus, the intermediate representation generator used in this work is a two phase process as opposed to single phase in previous work~\cite{pandita12:inferring, pandita13:WHYPER}. 
We next describe these two phases:

{\small $\bullet$} \textbf{POS Tags}: We first split a sentence into smaller constituent sentences based on the function of POS tags. 
For instance, consider the sentence which are then accurately annotated by the underlying NLP Parser:

@@

The Stanford parser faces difficulty to annotate accurately the Stanford-typed dependencies of the sentence because of presence of various clauses acting on various subject-object pairs.
As shown in Figure~\ref{fig:standep} the word ``including'' is annotated with Stanford-typed dependencies ``dep'' that is a catch all dependency. A catch all dependency is selected by a parser when no other appropriate dependency can be selected.
The \tool\ approach thus automatically break down the sentence into two smaller tractable sentences, which are accurately annotated:

@@

\begin{table*}
\begin{center}
\vspace*{-3ex}
\caption{Semantic Templates}
\vspace*{-1ex}

    \begin{tabular}{  l  p{5cm} p{10cm} }
    \topline
    \headcol  \textbf{S No.} 	& \textbf{Template} & \textbf{Summary} \\
    \midline

    		1. 		& Two sentences joined by a conjunction & Sentence is broken down into two individual sentences with the conjunction term serving as the connector between two. \\
\rowcol    	2. 		& Two sentences joined by a ``,''& Sentence is broken down to individual independent sentences \\
    		3.		& A noun phrase followed by another noun/pronoun/verb phrase in brackets & Two individual sentences are formed. The first sentence is the same as the parent sentence sans the noun/pronoun.verb phrase in bracket. The second sentence constitutes of the noun phrase followed by noun/pronoun/verb phrase without the brackets.\\
\rowcol    	4.		& A noun phrase by a conditional phrase in brackets & Two individual sentences are formed. The first sentence is the same as the parent sentence sans the conditional phrase in bracket. The second sentence constitutes of noun phrases followed by conditional in the bracket.\\ 
    		5.		& A conditional phrase followed by a sentence & Two dependent sentences are formed. The first sentence constitutes the conditional phrase. The second sentence constitutes rest of the sentence.\\
\rowcol    	6.		& A sentence in which the parent verb phrase is over two child verb phrases joined by a conjunction & Two dependent sentences are formed where the dependency is the conjunction. The first sentence is formulated by removing conjunction and second child verb phrase. The second sentence is formulated by removing conjunction and first child verb phrase. \\ 
\bottomlinec
    \end{tabular}
	\label{tab:semanticTemplates}
	\vspace*{-4ex}
\end{center}
\end{table*}

@@

\begin{figure}
	\begin{CodeOut}
		\begin{alltt}
			\hspace*{0.8in}01:before[6]
			\hspace*{0.8in}02:|->must be deleted[5]
			\hspace*{0.8in}03:\hspace*{0.2in}|->All[1]
			\hspace*{0.8in}04:\hspace*{0.2in}|\hspace*{0.2in}|->in[3]
			\hspace*{0.8in}05:\hspace*{0.2in}|\hspace*{0.4in}|->\textbf{objects}[2]
			\hspace*{0.8in}06:\hspace*{0.2in}|\hspace*{0.4in}|->\textbf{bucket}[4]
			\hspace*{0.8in}07:\hspace*{0.2in}|->can be deleted[8]
			\hspace*{0.8in}08:\hspace*{0.4in}|->\textbf{bucket}[7]
			\hspace*{0.8in}09:\hspace*{0.4in}|->\textbf{itself}[9]
		\end{alltt}
	\end{CodeOut}
	\vspace*{-3ex}
	\caption{\label{fig:FOLTree} FOL-like representation of the sentence \textit{``All objects in the bucket must be deleted before the bucket itself can be deleted.''}}
	\vspace*{-3ex}

\end{figure}

@@

\begin{enumerate}
\item \textit{Forward Operator ($\xi_1 \rightarrow \xi_2$)}: method call $\xi_1$ must be succeeded by method call $\xi_2$.

\item \textit{Backward Operator ($\xi_1 \leftarrow \xi_2$)}: method call $\xi_1$ must be preceded by method call $\xi_2$.

\item \textit{Negative Forward Operator ($\xi_1 \xrightarrow{-} \xi_2$)}: method call $\xi_1$ cannot be succeeded by method call $\xi_2$

\item \textit{Negative Backward Operator ($\xi_1 \xleftarrow{-} \xi_2$)}: method call $\xi_1$ cannot be preceded by the method call of $\xi_2$
\end{enumerate}
%The prohibition operators capture a different class of temporal constraints that cannot be
%expressed by the formulae constructed by previously proposed operators and their negations.
%For instance, the \textit{prohibition operators} seem to be negation of
%\textit{forward eventual operators} and \textit{backward eventual operators}.
%However, the negation of forward eventual operators is: not an invocation of $\xi_1$
%must be eventually followed by not an invocation of $\xi_2$. In contrast,
%\textit{prohibition operators} either negates antecedent or consequent but not both.
%In summary, we extended the formalism for temporal rules previously
%proposed by Lo et al.~\cite{lo2009mining} to express temporal constraints.

We next describe how \tool\ identifies the terms of the constraint formula:

@@

\textbf{Temporal Operator}:
\tool\ next identifies the direction (forward or backward) of the relationship by examining the tense of $\xi_2$ reference in the sentence.
Past tense is considered as backward and other tenses are considered as forward.
For instance, the sentence in Figure~\ref{fig:standep} since ``deleted'' is in past tense and therefore operator is backward and the constraint is 
Delete Bucket $\leftarrow$ Delete Object.
Negation is identified by presence of the negation verbs such as ``\textit{no}'', ``\textit{not}'', ``\textit{can't}'' ... etc.
Another rule for negation operator is if the sentence is in exception/error description.

@@

\begin{figure}
	\centering
	\includegraphics[scale=0.3]{KnowledgeGraph.eps}
	\vspace*{-2.5ex}
	\caption{Semantic Graph for the \CodeIn{Object} method in Amazon S3 REST API}
	\label{fig:knowledge}
	\vspace*{-3ex}
\end{figure}

### 2015-05-14 Draft/background.tex
Fixes #9
Formatted to fit in 10 page format
Closes #8

We next briefly introduce the NLP techniques used in this work that have been grouped into two broad categories.
We first introduce the core NLP techniques.
We then introduce the SE specific NLP techniques proposed in related work~\cite{pandita12:inferring,pandita13:WHYPER}.

@@

For instance, consider the word \CodeIn{POST}. 
The online Oxford dictionary %\footnote{\url{http://oxforddictionaries.com/us/definition/american_english/post?q=POST}}
has eight different definition of word \CodeIn{POST}, and none of them describes \CodeIn{POST} as an HTTP method\footnote{In HTTP vocabulary \CodeIn{POST} means: \textit{``Creates a new entry in the collection.
The new entry's URI is assigned automatically and is usually returned by the operation''}}
supported by REST API.
Thus existing POS tagging techniques fail to accurately annotate the POS tags of the sentences involving word \CodeIn{POST}.

>>>>

We next briefly introduce the NLP techniques used in this work that have been grouped into two broad categories.
We first introduce the core NLP techniques.
We then introduce the SE specific NLP techniques proposed in previous work~\cite{pandita12:inferring,pandita13:WHYPER}.

@@

For instance, consider the word \CodeIn{POST}. 
The online Oxford dictionary %\footnote{\url{http://oxforddictionaries.com/us/definition/american_english/post?q=POST}}
has eight generic definition of word \CodeIn{POST}, and none of them describes \CodeIn{POST} as an HTTP method\footnote{In HTTP vocabulary \CodeIn{POST} means: \textit{``Creates a new entry in the collection.
The new entry's URI is assigned automatically and is usually returned by the operation''}}
supported by REST API.
Existing POS tagging techniques that are trained on generic documents fail to accurately annotate the POS tags of the sentences involving word \CodeIn{POST}.

### 2015-05-14 Draft/conclusion.tex
Formatted to fit in 10 page format
Closes #8

\section{Conclusion}
\label{sec:conclusion}

Despite being highly desirable, formal temporal constraints are missing from most APIs.
In contrast, documentation of API methods contains detailed specifications of temporal constraints in natural language text.
Manually writing formal specifications based on natural language text in API documents is prohibitively time-consuming and error-prone.
To address this issue, we have proposed a novel approach called \tool\ to infer temporal constraints from natural language text of API documents.
We applied \tool\ to infer temporal constraints from
the \paypalAPI, the \amazonAPI, and the 
commonly used package \CodeIn{java.io} in the JDK API.
Our evaluation results show that \tool\ effectively identifies sentences describing
temporal constraints with an average 79\% precision and 60\% recall,
from more than 4000 sentences in subject API documents.
Furthermore, \tool\ also achieved an accuracy of
70\% in inferring 77 formal temporal constraints from these temporal constraint sentences.

>>>>

\section{Conclusion}
\label{sec:conclusion}
\vspace*{-1ex}
Despite being highly desirable, formal temporal constraints are missing from most APIs.
In contrast, documentation of API methods contains detailed specifications of temporal constraints in natural language text.
Manually writing formal specifications based on natural language text in API documents is prohibitively time-consuming and error-prone.
To address this issue, we have proposed a novel approach called \tool\ to infer temporal constraints from natural language text of API documents.
We used \tool\ to infer temporal constraints from
the \paypalAPI, the \amazonAPI, and the 
commonly used package \CodeIn{java.io} in the JDK API.
Our evaluation results show that \tool\ effectively identifies sentences describing
temporal constraints with an average 79\% precision and 60\% recall,
from more than 4000 sentences in subject API documents.
Furthermore, \tool\ also achieved an accuracy of
70\% in inferring 77 formal temporal constraints from these temporal constraint sentences.

### 2015-05-14 Draft/evaluation.tex
Formatted to fit in 10 page format
Closes #8

\begin{table*}
\begin{center}

\caption{Evaluation Results (Identification)}

\begin{tabular}{rlccccccccc}
\topline
\headcol S. No. & Trainer	& P$_{wrd}$	& R$_{wrd}$	& F$_{wrd}$	& P$_{ftr}$	& R$_{ftr}$	& F$_{ftr}$	& P$_{\Delta}$	& R$_{\Delta}$	& F$_{\Delta}$	\\
\midline 
			1	& AdaBoost			& 0.52	& 0.81	& 0.61	& 0.7	& 0.78	& 0.74	& 0.18	& -0.03	& 0.13	\\
\rowcol		2	& NaiveBayes		& 0.49	& 0.67	& 0.56	& 0.74	& 0.65	& 0.69	& 0.25	& -0.02	& 0.13	\\
			3	& Balanced Winnow	& 0.77	& 0.76	& 0.76	& 0.78	& 0.77	& 0.77	& 0.01	& 0.01	& 0.01	\\
\rowcol		4	& Decision Tree		& 0.82	& 0.58	& 0.66	& 0.92	& 0.41	& 0.56	& 0.1	& -0.17	& -0.1	\\
			5	& Winnow			& 0.19	& 0.41	& 0.15	& 0.8	& 0.51	& 0.59	& 0.61	& 0.1	& 0.44	\\
\rowcol		6	& MaxEnt			& 0.69	& 0.48	& 0.55	& 0.76	& 0.46	& 0.56	& 0.07	& -0.02	& 0.01	\\
			7	& c45				& 0.78	& 0.4	& 0.52	& 0.82	& 0.59	& 0.67	& 0.04	& 0.19	& 0.15	\\
\midline
			& Average			& 0.61	& 0.59	& 0.54	& 0.79	& 0.6	& 0.65	& 0.18	& 0.01	& 0.11	\\
\bottomlinec
%----------------- END TABLE DATA ------------------------ 
\multicolumn{11}{p{5in}}{\small
All values are average over 10-fold cross validation;
P: Precision; R: Recall; F: F-Score;
$_{wrd}$: No features used for training;
$_{ftr}$: features used for training;
$_{\Delta}$: improvement factor ($_{ftr}$ - $_{wrd}$)} \\ 
\end{tabular}
\label{tab:resultsRQ1}
\end{center}
\end{table*}

\begin{table}
\begin{center}

\caption{Evaluation Results (Inference)}

\begin{tabular}{lccccc}
\topline
\headcol 	API 			& Mtds 	& Sen 	& Sen$_C$ 	& Spec$_{ICON}$ 	& Acc(\%)\\
\midline 
			java.io 		& 662 	& 2417 	& 78 		& 56 				& 71.8\\ 
\rowcol 	Amazon S3 REST 	& 51 	& 1492 	& 12		& 7 				& 58.3\\ 
			Paypal REST 	& 33	& 151 	& 20 		& 14				& 70.0\\ 
\rowcol 	Total 			& 746 	& 4060 	& 110		& 77 				& 70.0$^*$\\ 
\bottomlinec
%----------------- END TABLE DATA ------------------------ 
\multicolumn{6}{p{3.25in}}{\small
$^*$ Average;
Mtds: Total no. of Methods; Sen: Total no. of Sentences; Sen$_C$: Total no. of constraint Sentences; Acc: Accuracy
Spec$_{ICON}$: Total no. of temporal constraints correctly identified by \tool;
} \\ 
\end{tabular}
\label{tab:results}
\end{center}
\end{table}

@@

In this section, we compared the temporal constraints inferred from the natural language API descriptions to those enforced by the type-system (referred to as type-enforced constraint).
The constraints that are enforced by the type-system can be enforced by IDEs.
Hence, for such types of constraints, we do not require sophisticated techniques like ICON. 
For \CodeIn{java.io}, we define a type-enforced constraint as a constraint that mandates a method $M$ accepting input parameter $I$ of type $T$ to be invoked after (at least one) a method $M'$ whose return value is of type $T$. 
Since there are no types in REST APIs, for \CodeIn{Amazon S3}, we consider a constraint as a type-enforced constraint
if the constraint is implicit in the \CodeIn{CRUD} semantic followed by REST operations. 
\CodeIn{CRUD} stands for resource manipulation semantic sequence create, retrieve, update, and delete.
In particular, we consider a constraint as a type-enforced constraint, if the constraint mandates a DELETE, GET, or PUT operation on a resource to be invoked after a POST operation on the same resource.

>>>>

\begin{table*}
\begin{center}
\vspace*{-3ex}
\caption{Evaluation Results (Identification)}
\vspace*{-1ex}
\begin{tabular}{rlccccccccc}
\topline
\headcol S. No. & Trainer	& P$_{wrd}$	& R$_{wrd}$	& F$_{wrd}$	& P$_{ftr}$	& R$_{ftr}$	& F$_{ftr}$	& P$_{\Delta}$	& R$_{\Delta}$	& F$_{\Delta}$	\\
\midline 
			1	& AdaBoost			& 0.52	& 0.81	& 0.61	& 0.7	& 0.78	& 0.74	& 0.18	& -0.03	& 0.13	\\
\rowcol		2	& NaiveBayes		& 0.49	& 0.67	& 0.56	& 0.74	& 0.65	& 0.69	& 0.25	& -0.02	& 0.13	\\
			3	& Balanced Winnow	& 0.77	& 0.76	& 0.76	& 0.78	& 0.77	& 0.77	& 0.01	& 0.01	& 0.01	\\
\rowcol		4	& Decision Tree		& 0.82	& 0.58	& 0.66	& 0.92	& 0.41	& 0.56	& 0.1	& -0.17	& -0.1	\\
			5	& Winnow			& 0.19	& 0.41	& 0.15	& 0.8	& 0.51	& 0.59	& 0.61	& 0.1	& 0.44	\\
\rowcol		6	& MaxEnt			& 0.69	& 0.48	& 0.55	& 0.76	& 0.46	& 0.56	& 0.07	& -0.02	& 0.01	\\
			7	& c45				& 0.78	& 0.4	& 0.52	& 0.82	& 0.59	& 0.67	& 0.04	& 0.19	& 0.15	\\
\midline
			& Average			& 0.61	& 0.59	& 0.54	& 0.79	& 0.6	& 0.65	& 0.18	& 0.01	& 0.11	\\
\bottomlinec
%----------------- END TABLE DATA ------------------------ 
\multicolumn{11}{p{5in}}{\small
All values are average over 10-fold cross validation;
P: Precision; R: Recall; F: F-Score;
$_{wrd}$: No features used for training;
$_{ftr}$: features used for training;
$_{\Delta}$: improvement factor ($_{ftr}$ - $_{wrd}$)} \\ 
\end{tabular}
\label{tab:resultsRQ1}
\vspace*{-5ex}
\end{center}
\end{table*}

\begin{table}
\begin{center}
\caption{Evaluation Results (Inference)}
\vspace*{-1ex}
\begin{tabular}{lccccc}
\topline
\headcol 	API 			& Mtds 	& Sen 	& Sen$_C$ 	& Spec$_{ICON}$ 	& Acc(\%)\\
\midline 
			java.io 		& 662 	& 2417 	& 78 		& 56 				& 71.8\\ 
\rowcol 	Amazon S3 REST 	& 51 	& 1492 	& 12		& 7 				& 58.3\\ 
			Paypal REST 	& 33	& 151 	& 20 		& 14				& 70.0\\ 
\rowcol 	Total 			& 746 	& 4060 	& 110		& 77 				& 70.0$^*$\\ 
\bottomlinec
%----------------- END TABLE DATA ------------------------ 
\multicolumn{6}{p{3.25in}}{\small
$^*$ Average;
Mtds: Total no. of Methods; Sen: Total no. of Sentences; Sen$_C$: Total no. of constraint Sentences; Acc: Accuracy
Spec$_{ICON}$: Total no. of temporal constraints correctly identified by \tool;
} \\ 
\end{tabular}
\label{tab:results}
\vspace*{-5ex}
\end{center}
\end{table}

@@

In this section, we compare the temporal constraints inferred from the natural language API descriptions to those enforced by the type-system (referred to as type-enforced constraint).
The constraints that are enforced by the type-system can be enforced by IDEs.
Hence, for such types of constraints, we do not require sophisticated techniques like ICON. 
For \CodeIn{java.io}, we define a type-enforced constraint as a constraint that mandates a method $M$ accepting input parameter $I$ of type $T$ to be invoked after (at least one) a method $M'$ whose return value is of type $T$. 
Since there are no types in REST APIs, for \CodeIn{Amazon S3}, we consider a constraint as a type-enforced constraint
if the constraint is implicit in the \CodeIn{CRUD} semantic followed by REST operations. 
\CodeIn{CRUD} stands for resource manipulation semantic sequence create, retrieve, update, and delete.
In particular, we consider a constraint as a type-enforced constraint, if the constraint mandates a DELETE, GET, or PUT operation on a resource to be invoked after a POST operation on the same resource.

### 2015-05-14 Draft/example.tex
Formatted to fit in 10 page format
Closes #8

\begin{figure}[t]
	\begin{center}
		\includegraphics[scale=0.45]{Stackoverflow.eps}
	\end{center}
	\caption{\label{fig:Stackoverflow} The Query posted on Stack Overflow forum regrading Amazon S3 REST API}
\end{figure}

Consider the question asked in \textit{Stack Overflow}~\footnote{{\small \url{http://stackoverflow.com/questions/27267/delete-amazon-s3-buckets}}} as shown in Figure~\ref{fig:Stackoverflow}.
Stack Overflow is an online question and answer forum for professional and enthusiast programmers.
The query is about the delete functionality of a third-party software \CodeIn{S3Fox} to interact with \amazonAPI.
The inquisitor complains about an issue in the delete bucket functionality of the \CodeIn{S3Fox}.
The \CodeIn{S3Fox} developers overlooked the constraints in \amazonAPI\ developer documents, causing the issue.
The API document pertaining to the  delete bucket functionality states that before deleting the bucket, the objects in the buckets must be deleted.
\textit{``All objects (including all objects versions and Delete Markers) in the bucket must be deleted before the bucket itself can be deleted''}.
Although the issue was fixed, one of the forum responses recommended the inquisitor to switch to another product.
Customer dissatisfaction caused by such issues with the delete bucket functionality can lead to a loss in revenue.

>>>>

\begin{figure}[t]
	\begin{center}
		\includegraphics[scale=0.45]{Stackoverflow.eps}
	\end{center}
	\vspace*{-3ex}
	\caption{\label{fig:Stackoverflow} Query posted on StackOverflow forum about Amazon S3 REST API}
	\vspace*{-3ex}
\end{figure}

Consider the question asked in \textit{Stack Overflow}~\footnote{ \url{http://stackoverflow.com/questions/27267/delete-amazon-s3-buckets}} as shown in Figure~\ref{fig:Stackoverflow}.
Stack Overflow is an online question and answer forum for professional and enthusiast programmers.
The query is about the delete functionality of a third-party software \CodeIn{S3Fox} to interact with \amazonAPI.
The inquisitor complains about an issue in the delete bucket functionality of the \CodeIn{S3Fox}.
The \CodeIn{S3Fox} developers overlooked the constraints in \amazonAPI\ developer documents, causing the issue.
The API document pertaining to the  delete bucket functionality states that before deleting the bucket, the objects in the buckets must be deleted.
\textit{``All objects (including all objects versions and Delete Markers) in the bucket must be deleted before the bucket itself can be deleted''}.
Although the issue was fixed, one of the forum responses recommended the inquisitor to switch to another product.
Customer dissatisfaction caused by such issues with the delete bucket functionality can lead to a loss in revenue.
